\section{Multi-rate signal processing}

A multi-rate processing system is a system that takes advantages of having multiple sample rates of the original signal. For instance a 48 kHz sample rate may be downsampled to 24 kHz. This also means that the highest frequency component that fulfills the Nyquist criterion is maximum 12 kHz. To avoid loss of data a highpass filter must be applied to the original signal such that the signal is split into two bands between 0 Hz to 24 kHz. The advantage of having a multi-rate system, is that the filter order for a filter is decreased for a downsampled subsystem. By doing so, the amount of computation is thus also decreased, but the disadvantage is an increase in delay from the filter. 

To downsample a signal, an anti-aliasing filter must first be applied. The purpose of the anti-aliasing filter is to filter higher frequencies components away, as aliasing will arise because of the Nyquist criterion. If not, a 13 kHz signal will appear as a 1 kHz signal if downsampling is performed without an anti-aliasing filter. A system consisting of both an anti-aliasing filter and a downsampler is called a decimator and the task is called decimation.

To upsample to a higher sampling rate an interpolator is needed. Interpolation is the opposite of decimation. The interpolator consist of an upsampler followed by an anti-aliasing. If the interpolation factor is desired to be 2 then the upsampler will insert a zero in-between each sample. This is afterwards filtered by an anti-aliasing filter to smooth the signal and gained with the upsampling factor.  

A multi-rate system is especially useful when implementing high order FIR-filters. The order of a FIR filter will be large if the impulse response of a FIR filter is long. By downsampling the signal, only a lower order FIR-filter is needed to achieve an equivalent filter response if filtered at the original $f_s$.



