\chapter{Listning Test}\label{app:journal_ListningTest}

This test was performed to investigated whether it is more pleasant to listen to a multi-band limiter or a single-band limiter. In order to give a broad selection of answers 10 people were randomly chosen to listen to four different types of music without knowing if they were listening to a multi-band limiter or single-band.

\section{Setup}

\begin{itemize}\addtolength{\itemsep}{-.35\baselineskip} 
\item A participant will be placed approximately 2-3 meters from the loudspeaker
\item The speaker will be driven by a Crown Studio Reference I amplifier.
\item The participant will be placed directly in front of a single speaker.
\item The power of the speaker will be adjusted to output a \gls{SPL} of approximately 80-83 dB(A).
\item The playback unit will be a computer.
\item The playback unit will be connected via. 3.5 mm mini jack cable to the amplifier.
\end{itemize}
\vspace{-5mm}
Furthermore the speaker will be placed in a listing room to give as natural a response as possible. The room conforms with the ITU-R BS775-1 standard for multichannel systems.

The clips used are originating from following songs:
\vspace{-5mm}
\begin{enumerate}\addtolength{\itemsep}{-.35\baselineskip} 
\item Shots \& Squats by Vigiland
\item Sultans Of Swings by Dire Straits
\item Stormy Weather by Teitur
\item Hearth Of Courage by Two Steps From Hell
\end{enumerate}
Test clips can be found on \path{CD://ListningTestFiles/RefX.wav} where X corresponds to the index number of the song.
The songs are mastered with the following effect blocks via Logic Pro:

\noindent\begin{minipage}[t]{0.5\linewidth}
    \textbf{Single-band:}
    \begin{itemize}\addtolength{\itemsep}{-.35\baselineskip} 
    \item 1 band in entire frequency spectrum
    \item 12 dB attenuation at 0 dBFS
    \item Attack time of 0.5 ms and release time of 1 ms
    \end{itemize}
    \end{minipage}%
    \begin{minipage}[t]{0.5\linewidth}
    \textbf{Multi-band:}
    \begin{itemize}\addtolength{\itemsep}{-.35\baselineskip} 
    \item 1 band from 0 to 100 Hz
    \item 1 band from 100 to 300 Hz
    \item 1 band from 300 to 1000 Hz
    \item 1 Limiter in entire frequency spectrum
    \item Attack time of 0.5 ms and release time of 1 ms
    \end{itemize}
\end{minipage}\par\bigskip
Test clips can be found on \path{CD://ListningTestFiles/} as \path{MultiX.wav} and \path{SingleX.wav} respectively where X corresponds to the index number of the song.



\subsection*{Setup}
The setup inside the room is done as displayed on \autoref{figure:SpeakertestSetupListning}. The participant is placed in a chair in front of one speaker.
\begin{figure}[H]
\centering
\tikzsetnextfilename{TestSetupListning}
\begin{tikzpicture}
\draw  (-3,2) rectangle (3,-1);
\draw  (2,1) rectangle (1,0);
\draw  (-2,0.5) ellipse (0.5 and 0.5);
\node at (-2,1.25) {Person};
\node at (1.5,1.25) {Speaker};
\end{tikzpicture}
\caption{Test setup}
\label{figure:SpeakertestSetupListning}
\end{figure}

\subsection*{Equipment used and AAU-no.}

\begin{table}[H]
\centering
\ra{1.3}
\begin{tabular}{S[table-format=1]ccc} \toprule
    {Item} & {Description} & {AAU-no} \\ \bottomrule 
    1      &  Monacor Sound Level Meter - SM-4      & 08132   \\
    4      &  Crown Studio Reference I Amplifier    & 52614   \\
    6      &  B \& K Microphone calibrator 4231     & 78301   \\
    8      &  Computer                              & NaN     \\  
    8      &  Passive Dali Zensor 5 AX              & NaN     \\ \bottomrule 
\end{tabular}
\caption{Table over equipment used in test}
\label{tab:UsedEquipmentListning}
\end{table}



\section{Procedure}\label{sec:SpeakerTestProcedure3}

The procedure for this test is described as follows:
\vspace*{-5mm}
\begin{enumerate}\addtolength{\itemsep}{-.35\baselineskip} 
\item Adjust volume of \gls{SPL} on all songs to approximately 80-83 dB.
\item Place test person in chair and explain procedure to him
\item Play \path{RefX.wav}
\item Play \path{MultiX.wav} and ask test subject to choose the most favourable clip.
\item Play \path{SingleX.wav} and ask test subject to choose the most favourable clip.
\item Repeat step 3 through 4 with the X on the file incremented.
\end{enumerate}

\section{Data Extraction}
The recordings can be found on:\\
\scalebox{0.7}{
\path{CD://ListningTestFiles/Lyttetest.excel}}\\
All of the data is inserted in tables where an x is the outcome. The tables are shown in raw format in section \ref{sec:rawdata_listning}.



\section{Raw data}\label{sec:rawdata_listning}
The following section shows the table of the outcomes. A is multi-band and B is single-band. The X marks the favoured track. 
\begin{figure}[H]
\centering
\begin{subfigure}[t]{0.20\textwidth}
\begin{table}[H]
\centering
\begin{tabular}{ccccc}
n        & A       & B       & A       & B      \\ \bottomrule 
1        & X       &         & X       &        \\
2        & X       &         & X       &        \\
3        & X       &         & X       &        \\
4        & X       &         &         & X      \\
5        & X       &         & X       &        \\ \hline
6        & X       &         &         & X      \\
7        & X       &         & X       &        \\
8        & X       &         & X       &        \\
9        & X       &         & X       &        \\
10       & X       &         & X       &        \\ \bottomrule 
\end{tabular}
\caption{Shots and Squats - Vigiland}
\label{tab:shotsandsquats}
\end{table}
\end{subfigure}
\hfill
\begin{subfigure}[t]{0.20\textwidth}
\begin{table}[H]
\centering
\begin{tabular}{ccccc}
n         & A        & B        & A       & B       \\ \bottomrule 
1         &          & X        & X       &         \\
2         & X        &          & X       &         \\
3         & X        &          & X       &         \\
4         & X        &          &         & X       \\
5         & X        &          & X       &         \\ \hline
6         &          & X        & X       &         \\
7         & X        &          & X       &         \\
8         & X        &          & X       &         \\
9         &          & X        &         & X       \\
10        & X        &          & X       &         \\ \bottomrule 
\end{tabular}
\caption{Sultans of swing - Dire Straits}
\label{tab:Sultansofswing}
\end{table}
\end{subfigure}
\hfill
\begin{subfigure}[t]{0.20\textwidth}
\begin{table}[H]
\centering
\begin{tabular}{ccccc}
n       & A      & B      & A      & B      \\ \bottomrule
1       & X      &        & X      &        \\
2       & X      &        & X      &        \\
3       & X      &        & X      &        \\
4       &        & X      &        & X      \\ 
5       & X      &        & X      &        \\ \hline
6       & X      &        & X      &        \\
7       & X      &        & X      &        \\
8       & X      &        & X      &        \\
9       & ?      & ?      & X      &        \\
10      & X      &        & X      &        \\ \bottomrule
\end{tabular}
\caption{Stormy Weather - Teitur}
\label{tab:stormyweather}
\end{table}
\end{subfigure}
\hfill
\begin{subfigure}[t]{0.20\textwidth}
\begin{table}[H]
\centering
\begin{tabular}{ccccc}
n          & A         & B         & A         & B        \\ \bottomrule
1          & X         &           & X         &          \\
2          & X         &           & X         &          \\
3          & X         &           & X         &          \\
4          & X         &           & X         &          \\ 
5          & X         &           & X         &          \\ \hline
6          & X         &           & X         &          \\
7          & X         &           & X         &          \\
8          & X         &           & X         &          \\
9          & X         &           & X         &          \\
10         & X         &           & X         &          \\ \bottomrule
\end{tabular}
\caption{Hearth of Courage - 2 Steps From Hell}
\label{tab:HearthofCourage}
\end{table}
\end{subfigure}

\caption{Tables showing what the test subjects asked. A symbols multi-band and B symbols single-band}
\label{tab:combinedanswers}
\end{figure}  

\vspace*{-5mm}
\section{Analysis}
The raw data is first visualized in a pie chart in \autoref{fig:piechartsongs}, which creates an overview of the distribution of favoured answers.
\begin{figure}[H]
\centering
\resizebox{0.5\textwidth}{!}{
\tikzsetnextfilename{Piechartsongs}
\begin{tikzpicture}
[
    pie chart,
    slice type={comet}{blu},
    slice type={legno}{rosso},
    slice type={coltello}{giallo},
    slice type={sedia}{viola},
    slice type={caffe}{verde},
    pie values/.style={font={\small}},
    scale=2
]
%    \pie{2008}{73/comet,13/legno,7/sedia,7/coltello}
%    \pie[xshift=2.2cm,values of coltello/.style={pos=1.1}]%
%        {2009}{52/comet,23/legno,17/sedia,3/coltello,5/caffe}
    \pie[values of caffe/.style={pos=1.1}]%
       {}{87.5/comet,10/legno,2.5/caffe}
%    \pie{2008}{87.5/comet,2.5/legno,10/sedia}
    \legend[shift={(1.5cm,0.5cm)}]{{Multiband}/comet, {Uncertain}/caffe, {Singleband}/legno}
%    \legend[shift={(3cm,-1cm)}]{{Chair (Manzano)}/sedia, {Coffee (Trieste)}/caffe}
\end{tikzpicture}}
\caption{Overall comparison of the answers}
\label{fig:piechartsongs}
\end{figure}

The raw data is further visualized in a bar chart showed in \autoref{fig:Barchartsongs} showing a more in-depth visualization according to each song. The bars are plotted showing the single-band and multi-band compared directly to each other.
\begin{figure}[H]
\centering
\tikzsetnextfilename{Barchartsongs}
\begin{tikzpicture}
\begin{axis}[
	width=3.0in,
	height=2.5in,
    ybar,
%    enlargelimits=0.15,
    legend style={at={(0.5,-0.15)},
      anchor=north,legend columns=-1},
    ylabel={no. of trails},
    symbolic x coords={Song 1,Song 2,Song 3,Song 4},
    xtick=data,
    ymin=0,
    ymax=23,
    nodes near coords,
    nodes near coords align={vertical},
    ]
\addplot coordinates {(Song 1,18) (Song 2,15) (Song 3,17) (Song 4,20)};
\addplot coordinates {(Song 1,2)  (Song 2,5)  (Song 3,2) (Song 4,0)};
\legend{Multiband,Singleband}
\end{axis}
\end{tikzpicture}
\caption{Comparison of the different test}
\label{fig:Barchartsongs}
\end{figure}

\autoref{fig:piechartsongs} shows a strong preference to the limitation of a multi-band limiter. Limitation of songs with a high dynamic range shows a pattern of being favourable with the mulit-band limiter. This correlates to the fact that the single-band distributes the compression across the whole spectrum and therefore giving a greater sensation of more compression. The result is a distorted sound. This is especially true for the 4th test song.


\section{Error sources}

There are two sources of error which could change the outcome of the result. The first error source is from the effect blocks used. They are not entirely identical with the system developed and might be different in perception. The most dominant error source is the amount of people used in the test. There are only 10 people used in the experiment which might not be a sufficient enough sample size.

\section{Conclusion}

The test showed a clear preference to the multi-band when subjected to songs in the genres, dance, acoustics, pop/rock and instrumental. It showed that the single-band limiter sounded too distorted hence not favourable. The multi-band limiter only compressed lower frequencies, and therefore less in the upper spectrum. This gives a sensation of less compression.



